\documentclass{article}


% if you need to pass options to natbib, use, e.g.:
\PassOptionsToPackage{numbers, compress}{natbib}
% before loading neurips_2024


% ready for submission
\usepackage[final]{neurips_2024}


% to compile a preprint version, e.g., for submission to arXiv, add add the
% [preprint] option:
%     \usepackage[preprint]{neurips_2024}


% to compile a camera-ready version, add the [final] option, e.g.:
%     \usepackage[final]{neurips_2024}


% to avoid loading the natbib package, add option nonatbib:
%     \usepackage[nonatbib]{neurips_2024}


\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.

\usepackage{lipsum}         %
\usepackage{todonotes}
\usepackage{subfigure}
\usepackage{algorithm}
% \usepackage{algorithmic}
\usepackage{algpseudocode}
\usepackage{tabulary}

\usepackage{xcolor}         % colors
\usepackage{microtype}
\usepackage{hyperref}
\usepackage{url}
\usepackage{booktabs}
\usepackage{microtype}
\usepackage{booktabs} % for professional tables
\usepackage{tabularray}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{amsthm}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{subcaption}
\usepackage{enumitem}
% \usepackage{geometry}
\usepackage{verbatim}
\usepackage{tcolorbox}
\usepackage{soul}
\usepackage{listings}

\usepackage{amssymb}%
\usepackage{pifont}%

% for appendix toc
\usepackage{minitoc}
\usepackage{booktabs}   

\input{math_commands.tex}

\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}

\newcommand{\cxh}[1]{\textcolor{purple}{cxh: #1}}
\newcommand{\yali}[1]{\textcolor{magenta}{[yali: #1]}}
\usepackage[defaultcolor = magenta, commandnameprefix=always]{changes}
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%

\AtBeginDocument{\setlength\abovedisplayskip{5pt}}
\AtBeginDocument{\setlength\belowdisplayskip{5pt}}

\usepackage{multirow}

\hypersetup{
    colorlinks=true,
    citecolor=blue,
    linkcolor=blue,
}


\input{pkgs/prompt_box.tex}


\usepackage{color}
\usepackage{colortbl}
\definecolor{mywhite}{gray}{.9}


\newcommand{\meanstd}[2]{$#1 {\scriptscriptstyle \pm #2}$}

\usepackage{authblk}

\title{Policy Learning from Tutorial Books \\ via Understanding, Rehearsing and Introspecting}


% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to LaTeX to determine where to break the
% lines. Using \AND forces a line break at that point. So, if LaTeX puts 3 of 4
% authors names on the first line, and the last on the second line, try using
% \AND instead of \And before the third author name.


\usepackage{authblk}

\author{%
  Xiong-Hui Chen\textsuperscript{1,}\thanks{~Equal Contribution. $^+$ Work done during Xiong-Hui Chen's visit at King's College London. \\ \textsuperscript{$\quad \quad \diamond$} Corresponding: yali.du@kcl.ac.uk,  yuy@nju.edu.cn,jun.wang@cs.ucl.ac.uk. } , 
  Ziyan Wang\textsuperscript{2,}$^*$, 
  Yali Du\textsuperscript{\rm 2, $\diamond$}, 
  Shengyi Jiang\textsuperscript{\rm 5}, 
  Meng Fang\textsuperscript{\rm 4}, 
  Yang Yu\textsuperscript{\rm 1, $\diamond$}, 
  Jun Wang\textsuperscript{\rm 3, $\diamond$}\\
  \textsuperscript{\rm 1} National Key Laboratory for Novel Software Technology, Nanjing University, China
\& School of Artificial Intelligence, Nanjing University, China \\
  \textsuperscript{\rm 2} King's College London, \textsuperscript{\rm 3} 	University College London,  \textsuperscript{\rm 4} University of Liverpool \\ \textsuperscript{\rm 5} The University of Hong Kong 
}



\begin{document}

\doparttoc % Tell to minitoc to generate a toc for the parts
\faketableofcontents % Run a fake tableofcontents command for the partocs

\maketitle

\begin{abstract}
    When humans need to learn a new skill, we can acquire knowledge through written books, including textbooks, tutorials, etc. However, current research for decision-making, like reinforcement learning (RL), has primarily required numerous real interactions with the target environment to learn a skill, while failing to utilize the existing knowledge already summarized in the text. The success of Large Language Models (LLMs) sheds light on utilizing such knowledge behind the books. 
    In this paper, we discuss a new policy learning problem called \textbf{P}olicy \textbf{L}earning from tutorial \textbf{B}ooks (\topic), which aims to leverage rich resources such as books and tutorials to derive a policy network. Inspired by how humans learn from books, we solve the problem via a three-stage framework: \textbf{U}nderstanding, \textbf{R}ehearsing, and \textbf{I}ntrospecting (URI). In particular, it first rehearses decision-making trajectories based on the derived knowledge after understanding the books, then introspects in the imaginary dataset to distill a policy network. 
    % We give the first practical implementation for each stage based on several advanced techniques of LLMs and RL.
    To validate the practicality of this methodology, we train a football-playing policy via URI and test it in the Google Football game. The agent can beat the built-in AI with a 37\% winning rate without interaction with the environment during training, while using GPT as the agent can only achieve a 6\% winning rate. Our project can be found at~\url{https://plfb-football.github.io/}.
    
    % Additionally, we have made  \href{https://anonymous.4open.science/r/URI_video_COLM/}{example gameplay recordings} available, providing a visual insight into our methodology's effectiveness.
\end{abstract}

\input{text/intro}

\input{text/related}


\input{text/method}


\input{text/experiment}

\input{text/conclusion}


\bibliography{example_paper}
\bibliographystyle{unsrtnat}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\appendix

\input{text/appendix}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{text/checklist}


\end{document}